Algorithms for Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2015-01-20 paper/paper.tex
added number of tasks in periodograms
Update acknowledgements

There are many applications that require scientific workflow ensembles.
CyberShake~\cite{Callaghan2011}, for example, uses ensembles to generate seismic
hazard maps.  Each workflow in a CyberShake ensemble generates a hazard curve
for a particular geographic location, and several hazard curves are combined to
create a hazard map.  In a 2013 study, CyberShake was used to generate a set
of hazard maps over 286 sites that required an ensemble of 2288
workflows~\cite{CyberShake13.4}. Similarly, users of Montage~\cite{Deelman2008}
often need several workflows  with different parameters to generate a set of
image mosaics that can be combined  into a single, large mosaic. The Galactic
Plane ensemble~\cite{GalacticPlane}, which generates several mosaics 
in different wavelengths, consists of 17 workflows,
each of which contains 900 sub-workflows.  Another ensemble example is the
Periodograms application~\cite{Vockler2011}, which searches for extrasolar
planets by detecting periodic dips in the light intensity of their host star.
Due to the large scale of the input data, this application is often split up
into multiple batches processed by different workflows. Additional workflows are
created to run the analysis using different parameters. A recent analysis of
Kepler satellite data required three ensembles of 15 workflows.

@@

\section*{Acknowledgments}
This work was supported by the NSF under award ACI-1148515 and
by the EU FP7 project VPH-Share (269978).

>>>>

There are many applications that require scientific workflow ensembles.
CyberShake~\cite{Callaghan2011}, for example, uses ensembles to generate seismic
hazard maps.  Each workflow in a CyberShake ensemble generates a hazard curve
for a particular geographic location, and several hazard curves are combined to
create a hazard map.  In a 2013 study, CyberShake was used to generate a set
of hazard maps over 286 sites that required an ensemble of 2288
workflows~\cite{CyberShake13.4}. Similarly, users of Montage~\cite{Deelman2008}
often need several workflows  with different parameters to generate a set of
image mosaics that can be combined  into a single, large mosaic. The Galactic
Plane ensemble~\cite{GalacticPlane}, which generates several mosaics 
in different wavelengths, consists of 17 workflows,
each of which contains 900 sub-workflows.  Another ensemble example is the
Periodograms application~\cite{Vockler2011}, which searches for extrasolar
planets by detecting periodic dips in the light intensity of their host star.
Due to the large scale of the input data, this application is often split up
into multiple batches processed by different workflows. Additional workflows are
created to run the analysis using different parameters. 
An example analysis of Kepler satellite data required three ensembles of 15 workflows, 
each workflow with about 14,000 tasks.

@@

\section*{Acknowledgments}
This work was supported by the U.S. Department of Energy Office of Science
under award number ER26110, by the National Science Foundation ACI SI2-SSI
program award number 1148515, and by the EU FP7 project VPH-Share (269978).
